---
layout: page
title: Photin
output:
  md_document:
    variant: gfm
    preserve_yaml: TRUE
cover-img: ["assets/img/Aix200_loading.jpg", "assets/img/Aix200RF_heat_up_test.jpeg", "assets/img/G1/G1_cntrl.JPG", "assets/img/G1/G1_GB_cntrl.JPG", "assets/img/G1/G1_side.JPG"]
#subtitle: Europe, Poland, Warsaw area
---

The company aim is to provide dedicated, fast and flexible MOCVD wafer growth services to worldwide customers in R&D and small scale production of compound semiconductor devices (InP / GaAs/ GaSb/ InAs ).  
<br>   
As **"Pure Play" MOCVD fab** we offer customers affordable development of epitaxial layer stacks on 2" substrates of choice (working on 3" capabilities) and full information on technology of growth processes and related data characterization.  
<br>   
The information shared include:  
- full data logs of Aixtron reactors (process temperatures, pressures, flows etc.)  
- full logs of MO lines equipped with ultrasonic in-situ gas delivery sensors (exact info on reagent flow to reactor)  
- full in situ monitoring data from LayTec EpiRAS or EpiCurve (true wafer temperature, RAS, reflectance or curvature), which provide unique fingerprint of process grown,  
- standard characterization data: HR XRD, 300K PL, Hall, ECV,  
- other relevant characterization data, are additionally offered as on request and are additionally charged (SIMS, XPS, SEM, TEM, AFM).  

<br>   
We do support our customers in technology transfer of developed process or device structure to large foundries or companies, that could offer benefits of large scale manufacturing and cost reduction out of reach for SME.  
<br>   
If needed we are happy to support customers also in area of device simulation and epitaxial design of lasers, LEDs, detectors, and solar cells (in house or via large network of specialists we have cooperate with).   
<br>   
Over the years, we have been working with/for AMS Sensors, AMS-OSRAM, Modulight, DenseLight, POET Technologies, VIGO System/Photonics, Brolis, Ensemble3, Bright Photonics, Huawei, Lancaster University, Institute of Microelectronics and Photonics (Poland), Military University of Technology (Poland).  
<br>   

```{r setup, include=FALSE}
library(stringr)
library(ggplot2)
library(rmarkdown)
library(knitr)

#cover-img: ../img/E0_with_bubblers.jpeg

```



```{r fig-options, include=FALSE}
base_dir <- "~/photin/beautiful-jekyll/" # i.e. where the jekyll blog is on the hard drive.
base_url <- "/" # keep as is

# If the document is currently being knit, do this; skip it in normal execution
if (!is.null(knitr::current_input())){
  
  # Output path for figures
  fig_path <- paste0("_site/assets/img/", str_remove(knitr::current_input(), ".Rmd"), "/")
  
  # Set base directories
  knitr::opts_knit$set(base.dir = base_dir, base.url = base_url)
  
  # Set figure directories
  knitr::opts_chunk$set(fig.path = fig_path,
                      cache.path = '../cache/',
                      message=FALSE, warning=FALSE,
                      cache = FALSE)
}
```
