---
title: Hero Dies - First Chips of III-V Semiconductor IR detectors
subtitle: "True Heroes Born Out of Passion!"
author: "Krzysztof Kłos"
date: "30/07/2025"
output:
  #pdf_document: default
  md_document:
    variant: gfm
    preserve_yaml: TRUE
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, 
  encoding = encoding, 
  output_file=paste0(Sys.Date(), "-", sub(".Rmd", ".md",inputFile)), 
  output_dir = "~/photin/krzyklo.github.io/_posts/") })
  
layout: post

cover-img: ["../assets/img/250208_InAs_photodiodes/hot_reactor.png", 
"../assets/img/250208_InAs_photodiodes/susceptor.png"]
thumbnail-img: /assets/img/250208_InAs_photodiodes/mesa1.png
share-img: /assets/img/250208_InAs_photodiodes/mesa1.png
tags: [news, MOCVD, InAs, InAsSbP, detector]
always_allow_html: true
---

```{r setup, include=FALSE}
library(stringr)
library(ggplot2)
library(rmarkdown)
library(knitr)
library(readr)

#cover-img: ../img/E0_with_bubblers.jpeg
```

```{r fig-options, include=FALSE}
base_dir <- "~/photin/krzyklo.github.io/" # i.e. where the jekyll blog is on the hard drive.
base_url <- "/" # keep as is

# If the document is currently being knit, do this; skip it in normal execution
if (!is.null(knitr::current_input())){
  
  # Output path for figures
  fig_path <- paste0("_site/assets/img/250208_InAs_photodiodes/", str_remove(knitr::current_input(), ".Rmd"), "/")
  
  # Set base directories
  knitr::opts_knit$set(base.dir = base_dir, base.url = base_url)
  
  # Set figure directories
  knitr::opts_chunk$set(fig.path = fig_path,
                      cache.path = '../cache/',
                      message=FALSE, warning=FALSE,
                      cache = FALSE)
}

```



### Hero Chips

Hero Chips or Hero Dies.. this phrase reference to research output, when most of the semiconductor wafer chips/dies are poor, broken, faulty, with particles, dust, errors due to lithography or has been overheated, overetched or under-etched, or metalization peeled off due to poor contacts.. countless reasons. Though, against all odds, the single few chips works regardless. Those single chips become true heroes. They are proof of concept for device or technology, and allow to write publication, grant report, show at conference, put on posters..., work further, secure more funds.
It doesn't matter that yield was in ppm range, not in %. If chip works, then it works! It is true hero, who could come forward, and fend off all critics and non-believers.  Anyone could take it and measure, and see themselves that the data are true, and hero is legit!

<iframe width="640" height="480" src="//www.youtube.com/embed/JHJ2e1H5J2s" frameborder="0" allowfullscreen="allowfullscreen">&nbsp;</iframe>

Like many true Heroes, those Hero Chips very often will suffer beyond imagination ;-). More than all others. They will be baked, boiled, sliced, torn apart, etched, uncapped, polished, bombarded with high energy beams of neutrons and ions, cut with lasers..
All that to take out from Heroes mystery! What it is that makes them so great, so special, and good??
Why they shine, when others failed?  
The name of our Hero here is 11261.  
**!! It is all made in Poland, epitaxy, processing, packaging!!  **
We suspect that also substrate, which come from old unbranded stock, is made in south Europe, so it is made in EU!  

In future we will make chips, which has higher responsivity, are easier to package and illuminate from the top = ring contacts like on this video.  

<iframe width="420" height="315" src="//www.youtube.com/embed/AG06h6FYE5I" frameborder="0" allowfullscreen="allowfullscreen">&nbsp;</iframe>  


### Key take away

No other Polish company, institute or university was able so far to showcase InAs ~3.5um detectors based on III-Sb semiconductors with better dark current performance than our reported results.  
Currently Photin ability to grow Sb-based, 6.1A family of III-V compounds in MOCVD provide researchers unique opportunities in SWIR/MWIR device development.

